---
output: html_document
runtime: shiny
---
<a name="home"></a>

# Probability Distributions 


## Continuous
- [Normal](/Probability_Distributions/probability_distributions_shiny.Rmd#normal)  
- [log-Normal](/Probability_Distributions/probability_distributions_shiny.Rmd#log-normal)  
- [t-](/Probability_Distributions/probability_distributions_shiny.Rmd#t-)  
- [F-](/Probability_Distributions/probability_distributions_shiny.Rmd#F-)  
- [Chi-square](/Probability_Distributions/probability_distributions_shiny.Rmd#chi-square)  
- [Beta](/Probability_Distributions/probability_distributions_shiny.Rmd#beta)  
- [Gamma](/Probability_Distributions/probability_distributions_shiny.Rmd#gamma)  

## Discrete 
- [Poisson](/Probability_Distributions/probability_distributions_shiny.Rmd#poisson)  
- [Binomial](/Probability_Distributions/probability_distributions_shiny.Rmd#binomial)  

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE)
```


<a name="normal"></a>

## Normal 
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("normal.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="log-normal"></a>

## log-Normal 
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("log-normal.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="t-"></a>

## t-
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("t.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="F-"></a>

## F-
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("F.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="chi-square"></a>

## Chi-square 
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("chi-square.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="beta"></a>

## Beta 
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("beta.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="gamma"></a>

## Gamma 
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("gamma.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="poisson"></a>

## Poisson 
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("poisson.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```

<a name="binomial"></a>

## Binomial 
[(Home)](/Probability_Distributions/probability_distributions_shiny.Rmd#home) 
```{r, echo=FALSE}
source("binomial.R")
shinyApp(ui = ui, server = server, options = list(height = 700, width = 900))
```


